On The Difficulty of Computing Non-Commutative Signature Gröbner Bases

### 2022-01-31 article_issac.tex
ex context free

>>>>

\begin{align*}
g_1 & := ssa - t\alpha x \\ 
g_2 & := xa - ax \\ 
g_3 & := xbb - \beta yb\\ 
g_4 & := yb-by\\ 
g_5 & := ycc-\gamma zc \\ 
g_6 & :=  \gamma z-z\gamma\\ 
g_7 & := bz-zb \\
g_8 & := \beta z-z\beta \\
g_9 & := az-za \\ 
g_{10} & := \alpha za-\alpha\alpha x  \\ 
g_{11} & := x\beta-\beta x\\ 
g_{12} & := xb-\beta y \\ 
g_{13} & := y\gamma-\gamma y \\
g_{14} & := \gamma o-oc \\
g_{15} & := oc-\gamma o \\ 
g_{16} & := \beta o-ob \\ 
g_{17} & := \alpha o-oa \\ 
g_{18} & := to-ss 
\end{align*}
